The Three-HITs Theorem

### 2017-03-27 Paper/Paper.tex
Reaplce `\Vdash` with `\vdash`.
Frege introduced `\vdash` more than a 100 years ago, so let's not change his notation
today. The symbol `\Vdash` is used in forcing and semantics, not in proof systems.

Next we define the notion of a constructor term.
\begin{definition}
\label{def:constructor-term}
Given is a function $c : A : T \rightarrow T$ with $A$ polynomial and $T$ a type.
Then we say $t$ is a \emph{constructor term} over $c$ if we can find polynomials $F$ and $G$ such that $x : F : T \Vdash t : G : T$ can be derived using the following rules.
\begin{gather*}
        \AxiomC{$t : B$}
        \AxiomC{$T$ does not occur in $B$}
        \BinaryInfC{$x:F : T \Vdash t : B$}
        \bottomAlignProof
        \DisplayProof 
         \quad
        \AxiomC{}
        \UnaryInfC{$x : F : T \Vdash x : F : T$}
        \bottomAlignProof
        \DisplayProof
        \quad
        \AxiomC{$x : F : T \Vdash r : A : T$}
        \UnaryInfC{$x : F : T \Vdash c : r : T$}
        \bottomAlignProof
        \DisplayProof
        \\[7pt]
        \AxiomC{$j \in \{1, 2\}$}
        \AxiomC{$x : F : T \Vdash r : G_1 : T \times G_2 : T$}
        \BinaryInfC{$x : F : T \Vdash\pi_j : r : G_j : T$}
        \bottomAlignProof
        \DisplayProof
        \quad
        \AxiomC{$j \in \{1, 2\}$}
        \AxiomC{$x : F : T \Vdash r_j : G_j$}
        \BinaryInfC{$x : F : T \Vdash (r_1, r_2) : G_1 : T\times G_2 : T$}
        \bottomAlignProof
        \DisplayProof
        \\[7pt]
        \AxiomC{$j \in \{1, 2\}$}
        \AxiomC{$x : F : T \Vdash r : G_j : T$}
        \BinaryInfC{$x : F : T : \inn_j : r : G_1 : T + G_2 : T$}
        \bottomAlignProof
        \DisplayProof
\end{gather*}
\end{definition}

@@

Before we can give the rules for higher inductive types, we need to define the lift of a constructor term.
\begin{definition}
Given is a constructor $c : A : H \rightarrow H$, a type family $Y : H \rightarrow \Type$, and a term $f : \prod (x: A : H), \bar{A} : Y : x \rightarrow  Y(c : x)$.
For a constructor term $F : H \Vdash r : G : H$ we define the \emph{lift $\dak{r}$ of $r$} with type 
$
x : F : H, h_x : \bar{F} : Y : x \vdash \dak{r} : \bar{G} : Y : r
$
by induction in $r$ as follows.
        \begin{align*}
                \dak{t} & := t
                & \dak{x} & := h_x &
                \dak{c_i : r} & := f_i : r : \dak{r}\\
                \dak{\pi_j : r} & := \pi_j : \dak{r} &
                \dak{(r_1, r_2)} & := (\dak{r_1}, \dak{r_2})
                & \dak{\inn_j : r} & := \dak{r}
        \end{align*}
\end{definition}

@@

\section{Lemmata}
\label{sec:Lemmata}
\begin{lemma}
\label{lem:constrTerm}
Suppose, we have a constructor term $t$ such that $x : F : T \Vdash t : G :T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow P$.
Then $t$ induces a map $\overline{t} : F : P \rightarrow H_{\Con}^n : (G : P)$ by replacing the constructors $c_{\nonrec}$ and $c_{\rec}$ by $c_{\nonrec}'$ and $c_{\rec}'$ respectively.
\end{lemma}

@@

\begin{lemma}
\label{lem:constrCoh}
Suppose, we have a constructor term $t$ such that $x : F : T \Vdash t : G : T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow Q$.
Furthermore, we assume that we have a map $f : Q \rightarrow P$
Then for all $x : F : P$ the terms $\overline{t}(F : f : x)$ and $(H_{\Con} \circ G) : f : (\overline{t} : x)$ are equal.
\end{lemma}

>>>>

Next we define the notion of a constructor term.
\begin{definition}
\label{def:constructor-term}
Given is a function $c : A : T \rightarrow T$ with $A$ polynomial and $T$ a type.
Then we say $t$ is a \emph{constructor term} over $c$ if we can find polynomials $F$ and $G$ such that $x : F : T \vdash t : G : T$ can be derived using the following rules.
\begin{gather*}
        \AxiomC{$t : B$}
        \AxiomC{$T$ does not occur in $B$}
        \BinaryInfC{$x:F : T \vdash t : B$}
        \bottomAlignProof
        \DisplayProof 
         \quad
        \AxiomC{}
        \UnaryInfC{$x : F : T \vdash x : F : T$}
        \bottomAlignProof
        \DisplayProof
        \quad
        \AxiomC{$x : F : T \vdash r : A : T$}
        \UnaryInfC{$x : F : T \vdash c : r : T$}
        \bottomAlignProof
        \DisplayProof
        \\[7pt]
        \AxiomC{$j \in \{1, 2\}$}
        \AxiomC{$x : F : T \vdash r : G_1 : T \times G_2 : T$}
        \BinaryInfC{$x : F : T \vdash\pi_j : r : G_j : T$}
        \bottomAlignProof
        \DisplayProof
        \quad
        \AxiomC{$j \in \{1, 2\}$}
        \AxiomC{$x : F : T \vdash r_j : G_j$}
        \BinaryInfC{$x : F : T \vdash (r_1, r_2) : G_1 : T\times G_2 : T$}
        \bottomAlignProof
        \DisplayProof
        \\[7pt]
        \AxiomC{$j \in \{1, 2\}$}
        \AxiomC{$x : F : T \vdash r : G_j : T$}
        \BinaryInfC{$x : F : T : \inn_j : r : G_1 : T + G_2 : T$}
        \bottomAlignProof
        \DisplayProof
\end{gather*}
\end{definition}

@@

Before we can give the rules for higher inductive types, we need to define the lift of a constructor term.
\begin{definition}
Given is a constructor $c : A : H \rightarrow H$, a type family $Y : H \rightarrow \Type$, and a term $f : \prod (x: A : H), \bar{A} : Y : x \rightarrow  Y(c : x)$.
For a constructor term $F : H \vdash r : G : H$ we define the \emph{lift $\dak{r}$ of $r$} with type 
$
x : F : H, h_x : \bar{F} : Y : x \vdash \dak{r} : \bar{G} : Y : r
$
by induction in $r$ as follows.
        \begin{align*}
                \dak{t} & := t
                & \dak{x} & := h_x &
                \dak{c_i : r} & := f_i : r : \dak{r}\\
                \dak{\pi_j : r} & := \pi_j : \dak{r} &
                \dak{(r_1, r_2)} & := (\dak{r_1}, \dak{r_2})
                & \dak{\inn_j : r} & := \dak{r}
        \end{align*}
\end{definition}

@@

\section{Lemmata}
\label{sec:Lemmata}
\begin{lemma}
\label{lem:constrTerm}
Suppose, we have a constructor term $t$ such that $x : F : T \vdash t : G :T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow P$.
Then $t$ induces a map $\overline{t} : F : P \rightarrow H_{\Con}^n : (G : P)$ by replacing the constructors $c_{\nonrec}$ and $c_{\rec}$ by $c_{\nonrec}'$ and $c_{\rec}'$ respectively.
\end{lemma}

@@

\begin{lemma}
\label{lem:constrCoh}
Suppose, we have a constructor term $t$ such that $x : F : T \vdash t : G : T$ which uses at most $n$ constructors, and that we have a map $c_{\nonrec}' : A_{\nonrec} \rightarrow Q$.
Furthermore, we assume that we have a map $f : Q \rightarrow P$
Then for all $x : F : P$ the terms $\overline{t}(F : f : x)$ and $(H_{\Con} \circ G) : f : (\overline{t} : x)$ are equal.
\end{lemma}
